Practical Type Flattening

### 2020-01-21 paper/paper.tex
propagate original types

We show that the techniques used for type reconstruction can be bypassed,
and we claim that the bypass is always possible given \emph{semantics gap} between
type systems of high-level and machine language.
% \keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{Introduction}
Binary code type recovery is to restore high-level type information of variables,
functions from machine codes. It is useful for reverse code engineering (e.g.
decompilation) or static binary rewriting/instrumentation, just to name a few.
Type recovery is available in several binary analysis
tools~\cite{noauthor_hex-rays_nodate, noauthor_jeb_nodate, noauthor_ghidra_nodate}
as a result of machine code decompilation. Academic research includes the classic
paper of Mycroft~\cite{mycroft_type-based_1999} which is probably the first work
on the domain, though earlier ideas~\cite{shivers_data-flow_1990} have been used
to recover types of programs in Scheme - a dynamically typed language.
Lee et al.~\cite{lee_tie_2011} introduces
an extension for Mycroft's work which supports a limited form of subtyping.
Caballero and Lin give a survey~\cite{caballero_type_2016} for research up until 2015.
Recent directions are using machine learning~\cite{maier_typeminer_2019} or statistical
language model~\cite{katz_estimating_2016}, which are out of scope of the paper.
All approaches tend to output a C-like type system.

Basically, the binary code type recovery starts by detecting high-level objects from
machine-dependent primitives: local variables are stored in function stack frame,
parameters are passed from registers, see~\cite{balakrishnan_wysinwyx_2007} for related techniques.
Type constraints are generated gradually through the \empĥ{low-level use} of objects.
The system of constraints is solved then, each object is assigned a certain
(polymorphic) type.

@@

\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.

Subsequent paragraphs, however, are indented.

\subsubsection{Sample Heading (Third Level)} Only two levels of
headings should be numbered. Lower level headings remain unnumbered;
they are formatted as run-in headings.

\paragraph{Sample Heading (Fourth Level)}
The contribution should contain no more than four levels of
headings. Table~\ref{tab1} gives a summary of all heading levels.

\begin{table}
\caption{Table captions should be placed above the
tables.}\label{tab1}
\begin{tabular}{|l|l|l|}
\hline
Heading level &  Example & Font size and style\\
\hline
Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
\hline
\end{tabular}
\end{table}

\noindent Displayed equations are centered and set on a separate
line.
\begin{equation}
x + y = z
\end{equation}
Please try to avoid rasterized images for line-art diagrams and
schemas. Whenever possible, use vector graphics instead (see
Fig.~\ref{fig1}).

\begin{figure}
\includegraphics[width=\textwidth]{fig1.eps}
\caption{A figure caption is always placed below the illustration.
Please note that short captions are centered, while long ones are
justified by the macro package automatically.} \label{fig1}
\end{figure}

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
% \begin{thebibliography}{8}
% \bibitem{ref_article1}
% Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

>>>>

We show that the techniques used for type reconstruction can be bypassed,
and we claim that the bypass is always possible given \emph{semantics gap} between
type systems of high-level and machine language.
% \keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{Introduction}
Binary code type recovery is to restore high-level type information of variables,
functions from machine codes. It is useful for reverse code engineering (e.g.
decompilation) or static binary rewriting/instrumentation, just to name a few.
Type recovery is available in several binary analysis
tools~\cite{noauthor_hex-rays_nodate, noauthor_jeb_nodate, noauthor_ghidra_nodate}
as a result of machine code decompilation. Academic research includes the classic
paper of Mycroft~\cite{mycroft_type-based_1999} which is probably the first work
on the domain, though earlier ideas~\cite{shivers_data-flow_1990} have been used
to recover types of programs in Scheme - a dynamically typed language.
Lee et al.~\cite{lee_tie_2011} extend Mycroft's work by introducing a form of
subtyping based on C's integer conversion rank, but lack of recursive type.
Polymorphic Type Inference for Machine Code.
Caballero and Lin give a survey~\cite{caballero_type_2016} for research up until 2015.
Recent directions are using machine learning~\cite{maier_typeminer_2019} or statistical
language model~\cite{katz_estimating_2016}, which are out of scope of the paper.
All approaches tend to output a C-like type system.

Basically, the binary code type recovery starts by detecting high-level objects from
machine-dependent primitives: local variables are stored in function stack frame,
parameters are passed from registers, see~\cite{balakrishnan_wysinwyx_2007} for related techniques.
Type constraints are generated gradually through the \emph{low-level use} of objects.
The system of constraints is solved then, each object is assigned a certain
(polymorphic) type.

@@

% \subsection{A Subsection Sample}
% Please note that the first paragraph of a section or subsection is
% not indented. The first paragraph that follows a table, figure,
% equation etc. does not need an indent, either.

% Subsequent paragraphs, however, are indented.

% \subsubsection{Sample Heading (Third Level)} Only two levels of
% headings should be numbered. Lower level headings remain unnumbered;
% they are formatted as run-in headings.

% \paragraph{Sample Heading (Fourth Level)}
% The contribution should contain no more than four levels of
% headings. Table~\ref{tab1} gives a summary of all heading levels.

% \begin{table}
% \caption{Table captions should be placed above the
% tables.}\label{tab1}
% \begin{tabular}{|l|l|l|}
% \hline
% Heading level &  Example & Font size and style\\
% \hline
% Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
% 1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
% 2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
% 3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
% 4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
% \hline
% \end{tabular}
% \end{table}

% \noindent Displayed equations are centered and set on a separate
% line.
% \begin{equation}
% x + y = z
% \end{equation}
% Please try to avoid rasterized images for line-art diagrams and
% schemas. Whenever possible, use vector graphics instead (see
% Fig.~\ref{fig1}).

% \begin{figure}
% \includegraphics[width=\textwidth]{fig1.eps}
% \caption{A figure caption is always placed below the illustration.
% Please note that short captions are centered, while long ones are
% justified by the macro package automatically.} \label{fig1}
% \end{figure}

% \begin{theorem}
% This is a sample theorem. The run-in heading is set in bold, while
% the following text appears in italics. Definitions, lemmas,
% propositions, and corollaries are styled the same way.
% \end{theorem}
% %
% % the environments 'definition', 'lemma', 'proposition', 'corollary',
% % 'remark', and 'example' are defined in the LLNCS documentclass as well.
% %
% \begin{proof}
% Proofs, examples, and remarks have the initial word in italics,
% while the following text appears in normal font.
% \end{proof}
% For citations of references, we prefer the use of square brackets
% and consecutive numbers. Citations using labels or the author/year
% convention are also acceptable. The following bibliography provides
% a sample reference list with entries for journal
% articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
% book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
% and a homepage~\cite{ref_url1}. Multiple citations are grouped
% \cite{ref_article1,ref_lncs1,ref_book1},
% \cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
% \begin{thebibliography}{8}
% \bibitem{ref_article1}
% Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)
